Software Ticket Quality

### 2017-10-30 proposal/mprop.tex
Add paper on information and system quality

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}\label{intro}

briefly explain the context of the project problem

@@

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}\label{intro}
briefly explain the context of the project problem

@@

\textbf{Antecedents of Information and System Quality}
\cite{nelson2005antecedents}:
\begin{itemize}
  \item \textbf{What were the goals?}
    The authors had 2 main research objectives they wanted to aim for in this
    paper:
      \begin{itemize}
        \item identify a set of antecedents that both drive information and
          system quality, as well as define the nature of the IT artifact;
        \item explore data warehousing in general, especially analytical tools,
          predefined reports and ad hoc queries.
        \end{itemize}
  \item \textbf{What was the method?}
    They conducted a cross-functional survey to test the model the authors 
    proposed. They focused on user experience with a data warehouse. They sent
    email invites to the Data Warehouse Institute which distributed it further
    to organizations, among which 7 agreed to participate, yielding a total of
    465 completed surveys. 
  \item \textbf{What did they learn?}
    They learned that their selected features were indeed a good indicator of
    overall information and system quality. They also found out that accuracy is
    the dominant determinant across all three data warehouse technologies, 
    followed by completeness and format. Also, the results showed that more 
    attention needs to be given to differences across varying technologies. 
  \item \textbf{Relevance to our work}: this paper presents important findings
    regarding information and system quality in an IT environment. We can use it
    when analysing the quality of the tickets we will mine.
\end{itemize}
